Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-04-14 article.tex
Add paragraphs
Render KS to supmat
Use bbbq_1 as sub-repo
Show simulated data more clearly
Add KS equation
Use KS equation

@@

@@

@@

We compare these distribution using a two-sample 
Kolmogorov-Smirnov (KS) test. The KS test determines if two samples
are derived from a same distribution, without making assumptions
regarding the shape of that distribution. We will reject
the null hypothesis that MHC-I has the same percentage of epitopes 
overlapping with TMHs in Homo sapiens as in COVID-19 when 
the KS statistic follows the relationship as show in 
figure \ref{fig:ks}, for an $\alpha$ of $0.05$.
is below

\begin{figure}[!htbp]
  \includegraphics[width=0.4\textwidth]{pics/ks.png}
  \caption{
    Condition of a Kolmogorov-Smirnov (KS) statistic to rejects a null
    hypothesis. $D_{n,m}$ is the KS statistic, $n = m$ is the size
    of the samples, in this case, the number of HLA haplotypes ($n = m = 13$).
    $\alpha = 0.05$ is the significance level.
  }
  \label{fig:ks}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{ks/fig_1_watermarked.png}
  \caption{
    \% epitopes overlapping with transmembrane helix
    for a human and COVID-19 proteome
  }
  \label{fig:1}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Binding}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table}
  \input{ks/table_1.latex}
  \caption{Percentage of MHC-I epitopes overlapping with transmembrane helix}
  \label{table:1}
\end{table}

>>>>

\paragraph{MHC-I}

@@

\paragraph{MHC-II}

@@

\paragraph{Evolution}

@@

We compare these distribution using a two-sample 
Kolmogorov-Smirnov (KS) test. The KS test determines if two samples
are derived from a same distribution, without making assumptions
regarding the shape of that distribution.

We will reject
the null hypothesis that MHC-I has the same percentage of epitopes 
overlapping with TMHs in Homo sapiens as in COVID-19 when 
the KS statistic $D_{n,m}$ follows the relationship as shown in 
equation \ref{eq:ks}, for a significance level $\alpha = 0.05$
and $n = m = 13$ HLA haplotypes.

\begin{equation}
   D_{n,m} > \frac{1}{\sqrt{n}} \cdot \sqrt{ -\ln(\frac{\alpha}{2}) \cdot \frac{1 + \frac{n}{m}}{2} }
\  \label{eq:ks}
\end{equation}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_1/fig_bbbq_1_watermarked.png}
  \caption{
    \% epitopes overlapping with transmembrane helix
    for a human and COVID-19 proteome
  }
  \label{fig:1}
\end{figure}

@@

\begin{table}
  \input{bbbq_1/bbbq_1_percentages.latex}
  \caption{
    Percentage of MHC-I epitopes overlapping with transmembrane helix.
    \richel{This is simulated data}
  }
  \label{table:1}
\end{table}

\begin{table}
  \input{bbbq_1/bbbq_1_stats.latex}
  \caption{
    Kolmogorov-Smirnov test results
    \richel{Done on the simulated data}
  }
  \label{table:ks}
\end{table}
